Measuring individual differences in the understanding of gaze cues across the lifespan

### 2022-03-22 paper/manuscript.Rmd
add age model

```{r fig2, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab2)"}
knitr::include_graphics(c("../figures/gafo_results.png"))
```

>>>>

```{r fig2, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab2)"}
knitr::include_graphics(c("../figures/gafo_results.png"))
``` 
```{r}
mAgeHedge <- readRDS(file = "../stats/mAgeHedge.rds") 
mAgeBox <- readRDS(file = "../stats/mAgeBox.rds") 
```

We assessed the effect of data collection mode and age (in months, z-transformed) in a Bayesian generalized linear mixed model with target position and subject ID as random effects. In the hedge version, the estimate of age was `r fixef(mAgeHedge)["age", "Estimate"]` ([`r fixef(mAgeHedge)["age", "Q2.5"]`; `r fixef(mAgeHedge)["age", "Q97.5"]`]) and the estimate of data collection mode was `r fixef(mAgeHedge)["datacollectionremoteMunsupervised", "Estimate"]` ([`r fixef(mAgeHedge)["datacollectionremoteMunsupervised", "Q2.5"]`; `r fixef(mAgeHedge)["datacollectionremoteMunsupervised", "Q97.5"]`]; with remote unsupervised data collection as the reference category). 
In the box version, the estimate of age was `r fixef(mAgeBox)["age", "Estimate"]` ([`r fixef(mAgeBox)["age", "Q2.5"]`; `r fixef(mAgeBox)["age", "Q97.5"]`]) and the estimate of data collection mode was `r fixef(mAgeBox)["datacollectionremoteMunsupervised", "Estimate"]` ([`r fixef(mAgeBox)["datacollectionremoteMunsupervised", "Q2.5"]`; `r fixef(mAgeBox)["datacollectionremoteMunsupervised", "Q97.5"]`]; remote unsupervised data collection as reference category).

### 2022-03-22 paper/manuscript.tex
add age model

>>>>

We assessed the effect of data collection mode and age (in months, z-transformed) in a Bayesian generalized linear mixed model with target position and subject ID as random effects. In the hedge version, the estimate of age is -0.33 ({[}-0.42; -0.23{]}) and of data collection mode is -0.32 ({[}-0.50; -0.14{]}, with remote unsupervised data collection as the reference category).
In the box version, the estimate of age is 0.64 ({[}0.41; 0.88{]}) and of data collection mode is 1.16 ({[}0.73; 1.61{]}, with remote unsupervised data collection as the reference category).
